---
title: "Project Presentation"
output: html_notebook
---

```{r}
library(dplyr)
require(tidyverse)
require(lattice)
dataset=read.csv('Parks.csv')

dataset$date <- sapply(strsplit(as.character(Dataset$Date.and.Time), " "), "[", 1)
#Dataset$Date<-as.factor(Dataset$Date)



dataset
```
```{r}
dataset$Attendance=as.numeric(gsub(",","",dataset$Attendance))
dataset
dataset%>%is.na()%>%colSums()
sum(dataset%>%is.na()%>%rowSums()>0)


```
```{r}

dataset$Attendance<-as.numeric(dataset$Attendance)
typeof(dataset$Attendance)
mean<-mean(dataset$Attendance,na.rm = TRUE)
round(mean)




```


```{r}

dataset<-dataset%>%mutate(Attendance=replace_na(Attendance, mean(Attendance, na.rm = TRUE)))
dataset<-dataset%>%mutate(Attendance=round(Attendance))
dataset%>%is.na()%>%colSums()
```




```{r}

ave_Attend=dataset%>%group_by(Event.Type)%>%summarise(ave_Attendance=mean(Attendance))
ave_Attend
barchart(Event.Type~ave_Attendance, data=ave_Attend)
```

#2)New column=aging of the events.Attendance based on earlier events v/s recents events- which were the 10 events with maximum attendance (most populated) and 10 events with minimum attendance (least populated)
```{r}
today <- Sys.Date()
today<-format(today,format="%m/%d/%Y")
today
Date1<-today
Date2<-dataset$date

dataset$Age<- as.Date(as.character(Date1), format="%m/%d/%Y")-
                  as.Date(as.character(Date2), format="%m/%d/%Y")  
dataset

recent_Events<-head(dataset)
recent_Events
old_Events<-tail(dataset)
old_Events

```





```{r}
Age_of_Events<-as.numeric(dataset$Age)
xyplot(Event.Type~(Age_of_Events),data=dataset)



```
#3)From which borough of New york city is the maximum and minimum attendance coming?
```{r}
ggplot(dataset, aes(x=Borough, y=Attendance)) + geom_point(size=4,shape=23,color="RED")+theme_bw()

```
#4)Total numbers of events by month - which month hit maximum number of events or which month hit minimum number of events?

```{r}
Date3<-dataset$Date
Date3<-as.Date(Date3,format ="%m/%d/%Y")
dataset$year <- as.numeric(format(Date3,'%Y'))

Date4<-dataset$Date
Date4<-as.Date(Date4,format ="%m/%d/%Y")
dataset$month <- as.numeric(format(Date3,'%m'))
dataset$month <- as.character(format(Date4,'%B'))

dataset


```









```{r}

dataset

Event<-as.factor(dataset$Event.Type)
Event<-as.numeric(Event)
df<-dataset%>%count(month,'Event')
df

ggplot(data = df, aes(x = factor(month,levels=month.name), y = n)) +
      geom_bar(stat = "identity", fill = "maroon") +
      labs(title = "Total Number of Events in Month",
           x = "Month", y = "No. of Events")+theme_classic()



```

6)What was the location type or unit with maximum attendance/minimum attendance?
```{r}
typeof(dataset$Attendance)
dataset$Attendance<-as.numeric(dataset$Attendance)
ave_attendance=dataset%>%group_by(LocationType)%>%summarise(ave_attend=as.numeric(mean(Attendance),na.rm=TRUE))
ave_attendance
ave_attend<-c(145.00,127.83347,169.46004,155.20000,89.82664,74.83333)
pct <- round(ave_attend/sum(ave_attend)*100)

lbls <- paste(ave_attendance$LocationType, pct)
lbls <- paste(lbls,"%",sep="") 
colors = c("red", "yellow", "green", "purple", "blue", "pink") 
pie(ave_attendance$ave_attend, labels=lbls, col=colors, main="Distribution of Attendance by Location Type" )

 
```
```{r}

histogram(~Attendance|as.factor(year),data=dataset,main="Attendance Distribution by Years")



```
#Attendance by age and Event.Type by age
```{r}


ggplot(data = ave_Attend) + 
  geom_point(mapping = aes(x = Age, y = ave_Attendance,color=Event.Type,))+labs(x="Age_of_Events(Days)",y="Attendance")





```
#Which were the busiest Events
```{r}
dataset%>%select(Category,Attendance)%>%filter(Attendance>1000)%>%arrange(desc(Attendance))

  
```
```{r}
dataset1<-dataset%>%select(Attendance,Age)%>%filter(Age<334)
dataset2<-dataset%>%select(Attendance,Age)%>%filter(Age>1150)
dataset3<-rbind(dataset1,dataset2)
dataset3
ggplot(data = dataset3, aes(x = Age, y = Attendance)) +
      geom_line(stat = "identity") +
      labs(x = "Age", y = "Attendance")


```

```{r}

data<-dataset%>%select(Attendance,year)%>%filter(year==2017)
Total1<-mean(data$Attendance)
round(Total1)
data1<-dataset%>%select(Attendance,year)%>%filter(year==2018)
Total2<-mean(data1$Attendance)
round(Total2)
data2<-dataset%>%select(Attendance,year)%>%filter(year==2019)
Total3<-mean(data2$Attendance)
round(Total3)
Total<-sum(Total1,Total2,Total3)
round(Total)

percent<-(Total1/Total)*100
round(percent)

percent2<-(Total2/Total)*100
round(percent2)

percent3<-(Total3/Total)*100
round(percent3)



```

















